Quality measure notes

### 2021-09-20 StateOfPractice/Ao-Report/11Introduction.tex
MI report - updated according to the external review

\section{Overview of the Methodology}
We designed a general method to assess the state of the practice for SC software. With this method, we choose an SC domain and identify software candidates in it. Then, we filter the candidates and produce a final list of about 30 software packages. We measure the qualities of each software by answering questions on a grading template, as shown in Appendix \ref{ap_grading_template}. With the quantitative data generated by the template, we rank the software with the Analytic Hierarchy Process (AHP). After that, we interview some of the development teams to further understand the status of their development process. Finally, we summarize the results and propose recommendations for future SC software development.

>>>>

\section{Overview of the Methodology}
We designed a general method to assess the state of the practice for SC software. With this method, we choose an SC domain and identify software candidates in it. Then, we filter the candidates and produce a final list of about 30 software packages. We measure the qualities of each software by answering questions on a grading template, as shown in Appendix \ref{ap_grading_template}. Comparing with our previous research mentioned in Section \ref{sec_motivation}, this project includes a new type of measurement, the empirical measurements, in the grading template. We use the empirical measurements to collect metrics from project repositories and source code. With the quantitative data generated by the template, we rank the software with the Analytic Hierarchy Process (AHP), which is a technique for group decision-making in complex situations. Section \ref{sec_AHP} includes description about the AHP. After that, we interview some of the development teams to further understand the status of their development process. Finally, we summarize the results and propose recommendations for future SC software development.
